### 2013-12-17 tests_Auto-Mpg.Rmd
added 'load' commands to tests_*.Rmd
testing tuning Auto-MPG

@@

>>>>

load(file="Auto-Mpg300_lambda0.8_add_linears.Rda")
load(file="Auto-Mpg300_lambda1_allmonoids.Rda")
summary(report$ga.error)

@@

########################################################
# Tuning SVM & RPART

rsme <- function(v1, v2=c(0)) {
  sqrt(mean((v1-v2)^2))
}

library(e1071)

head(my.data,8)

n.runs <- 25
train.p.size <- 0.7 # percentage of training set

svm.error <- rep(NA,n.runs)
rpart.error <- rep(NA,runs)

for (i in 1:n.runs) {
  inTrain   <- sample(1:nrow(my.data), train.p.size * nrow(my.data))
  train.set <- my.data[inTrain,]
  test.set  <- my.data[-inTrain,]

  svm.tune <- tune.svm(y ~ ., data=train.set)
  svm.pred  <- predict(svm.tune$best.model, test.set[,-ncol(test.set)]) 
  svm.error[i] <- rsme(svm.pred,test.set[,ncol(test.set)])

  rpart.tune <- tune.rpart(y ~ ., data=train.set)
  rpart.pred  <- predict(rpart.tune$best.model, test.set[,-ncol(test.set)]) 
  rpart.error[i] <- rsme(rpart.pred,test.set[,ncol(test.set)])
}
